### 2024-02-18 sections/2homology.tex
Add files via upload

---------------

@@

    For the purposes of the proof introduce the shorthand notation $\mathscr{D} := \disk(\mathsf{D}_1^{\partial, *})$. There is a functor $\Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}}$ from the opposite of the simplex category, whose essential image consists of those objects for which the distinguished subsets with a maximal and minimal element are non-empty. This functor is final\footnote{A functor $F: \catC \xrightarrow{} \mathscr{D}$ between $\infty$-categories is final if precomposition with it preserves colimits \[ \mathsf{colim}(G \circ F) \simeq \mathsf{colim}(G).\]} because adjoining a minimum and maximum gives a left adjoint to it. We recognize the simplicial object
    %
    \begin{equation}
        \mathsf{B}_{\bullet}(R, A, L): \Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}} \simeq \mathscr{D}_{/[-1,1]} \xrightarrow{} \mathscr{D} \xrightarrow{(R, A, L)} \catC
    \end{equation}
    %
    as the two-sided bar construction. Since $\catC$ has colimits and $\Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}}$ is final, the geometric realization of the above is
    %
    \begin{equation}
        \mathsf{B} (R, A, L) \equiv R \bigotimes\limits_{A} L = |\mathsf{B}_{\bullet}(R, A, L)| \simeq \mathsf{colim} (\mathscr{D}_{/[-1,1]} \xrightarrow{} \mathscr{D} \xrightarrow{(R, A, L)} \catC) = \int_{[-1,1]} (R, A, L).
    \end{equation}
    %
    To show the naturality of these equivalences, in the algebra variable, consider the algebra map $(F \xrightarrow{f} G) \in \mathsf{Fun}(\disk_{/[-1,1]}, \catC)$. We can consider the colimit as a functor
    %
    \begin{equation}
        \mathsf{colim}: \mathscr{C} \mathsf{at}_{\infty / \catC} \xrightarrow{} \catC,
    \end{equation}
    %
    such that the equivalences arise from composing with the adjoints $\Delta^{\mathsf{op}} \mathrel{\substack{\textstyle\leftarrow\\[-0.1ex]\textstyle\hookrightarrow}} \disk_{/[-1,1]}$. The naturality condition is then arranged by the functoriality of $\mathsf{colim}$, namely, by the images of the squares
    %
    \begin{equation}
        \begin{tikzcd}[row sep = small]
            \Delta^{\mathsf{op}} \arrow[r, hook, shift right] \arrow[dd, equal] & \disk_{/[-1,1]} \arrow[rd, "F"] \arrow[l, shift right] \arrow[dd, phantom, bend left = 60, "f"] \arrow[dd, equal] & \\
            & & \catC \\
            \Delta^{\mathsf{op}} \arrow[r, hook, shift right] & \disk_{/[-1,1]} \arrow[ru, "G"'] \arrow[l, shift right] &  
        \end{tikzcd}
    \end{equation}
    %
    over $\catC$.
\end{proof}

%\begin{proposition}[{\cite[prop.2.34]{aft_fhstrat}}]\label{prop:barconst=intinterval}
%    Let $A$ be a unital, (homotopy) associative algebra in $\catC$, $R$ be a unital right $A$-module in $\catC$ and $L$ be a unital left $A$-module in $\catC$. Using \cref{prop:disk1bor=assocRL} regard this data as the data of a symmetric monoidal functor $(R, A, L): \disk (\mathsf{D}_1^{\partial, *}) \xrightarrow{} \catC$. Then there is a canonical equivalence in $\catC$ between factorization homology over the closed interval and the two-sided bar construction
%    %
%    \begin{equation}
%        \int_{[-1,1]} (R, A, L) \xrightarrow{\ \ \simeq \ \ } R \bigotimes\limits_{A} L.
%    \end{equation}
%\end{proposition}

@@

>>>>

\begin{remark}\label{rem:fin_equiv_natural}
    A few times in this work we will encounter the fact that a final functor $F: \mathscr{A} \xrightarrow{} \mathscr{B}$ between $\infty$-categories induces an equivalence
    %
    \begin{equation}\label{eq:fin_equivs_obj}
        \mathsf{colim}(G) \xrightarrow{\ \ \simeq \ \ } \mathsf{colim}(G \circ F),
    \end{equation}
    %
    for each functor $G: \mathscr{B} \xrightarrow{} \mathscr{C}$, whenever both colimits exist. We remark here that these equivalences are actually even natural in $G$. To explain this, we first notice that the equivalences in \cref{eq:fin_equivs_obj} actually arise from equivalences between $\infty$-categories
    %
    \begin{equation}\label{eq:fin_equivs_cat}
        \mathscr{C}_{G/} \xrightarrow{\ \ \simeq \ \ } \mathscr{C}_{G \circ F /},
    \end{equation}
    %
    as discussed in \cite[prop.4.1.1.8]{lurie_htt}, where the functor is the obvious one. Furthermore, \cite[\href{https://kerodon.net/tag/016H}{016H}]{lurie_kerodon} tells us that the coslice construction is functorial, which for our purposes defines the functors
    %
    \begin{align}
        &S: \mathsf{Fun}(\mathscr{B}, \mathscr{C}) \xrightarrow{\ \ \ } \cat& \mathrm{and}& &S': \mathsf{Fun}(\mathscr{A}, \mathscr{C}) \xrightarrow{\ \ \ } \cat,&
    \end{align}
    %
    whose value on objects is given by $G \mapsto \mathscr{C}_{G/}$. We can now state that by naturality in $G$ we mean that the functors \cref{eq:fin_equivs_cat} assemble into an equivalence of functors   
    %
    \begin{equation}
        S \xrightarrow{\ \ \simeq \ \ } S' \circ F^*
    \end{equation}
    %
    in $\mathsf{Fun}(\mathsf{Fun(\mathscr{B}, \mathscr{C})}, \cat)$. But this is obviously the case, given the description of the maps in \cref{eq:fin_equivs_cat}.
\end{remark}

@@

    For the purposes of the proof introduce the shorthand notation $\mathscr{D} := \disk(\mathsf{D}_1^{\partial, *})$. There is a functor $\Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}}$ from the opposite of the simplex category, whose essential image consists of those objects for which the distinguished subsets with a maximal and minimal element are non-empty. This functor is final because adjoining a minimum and maximum gives a left adjoint to it. We recognize the simplicial object
    %
    \begin{equation}
        \mathsf{B}_{\bullet}(R, A, L): \Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}} \simeq \mathscr{D}_{/[-1,1]} \xrightarrow{} \mathscr{D} \xrightarrow{(R, A, L)} \catC
    \end{equation}
    %
    as the two-sided bar construction. Since $\catC$ has colimits and $\Delta^{\mathsf{op}} \xhookrightarrow{} \mathsf{O^{RL}}$ is final, the geometric realization of the above is
    %
    \begin{equation}
        \mathsf{B} (R, A, L) \equiv R \bigotimes\limits_{A} L = |\mathsf{B}_{\bullet}(R, A, L)| \simeq \mathsf{colim} (\mathscr{D}_{/[-1,1]} \xrightarrow{} \mathscr{D} \xrightarrow{(R, A, L)} \catC) = \int_{[-1,1]} (R, A, L).
    \end{equation}

    Since the equivalences above come from an argument about finality, \cref{rem:fin_equiv_natural} tells us that they are actually even natural in the algebra variable $(R, A, L)$, so that the equivalence lifts to the level of functors.
\end{proof}

@@

\begin{remark}\label{rem:fh_pushforward_functorial}
    As was the case with the bar construction the equivalence of \cref{thm:fh_pushforward}, comes about through an argument about a final functor, this means that, through \cref{rem:fin_equiv_natural} there is even an equivalence between functors
    %
    \begin{equation}
        \int_M -, \int_N f_* - : \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \ \ } \catC.
    \end{equation}
\end{remark}

### 2024-02-18 sections/3algebras.tex
Add files via upload

\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given $M$ a stratified manifold factorization homology provides a functor between the $\infty$-categories of $\disk_M$-algebras and locally constant factorization algebras $\lcfa_M$
    %
    \begin{equation}
        \int : \alg{\disk_M} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
    \end{equation}
\end{proposition}

@@

    Since $\catC$ has all relevant colimits the left Kan extension $\int F$ is given pointwise by
    %
    \begin{equation}\label{eq:pointwiseKan}
        \int_e F \simeq \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
    \end{equation}
    %
    so what we need to show is that this colimit is equivalent to the colimit
    %
    \begin{equation}\label{eq:cosheaf_colim_relative}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \rightarrow \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    for each covering sieve $\mathscr{U}$. Since we aren't actually trying to get the value of these colimits we can rewrite \cref{eq:pointwiseKan} into the idiosyncratic form
    %
    \begin{equation}\label{eq:idiosync_form}
        \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    which is easier to compare to \cref{eq:cosheaf_colim_relative}. Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalences of \cref{lem:double_slice} we can rewrite \cref{eq:idiosync_form} further into
    %
    \begin{align}
        \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC) \\ \simeq \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC).
    \end{align}
    %
    Denoting the functor $\mfld[r]_{/N} \simeq (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC$ by $K_F$ and comparing with \cref{eq:cosheaf_colim_relative} we need to show
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C) \simeq \mathsf{colim} (\disk[r]_{N} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C),
    \end{equation}
    %
    but this already follows from part 2 of the proof of \cite[prop.2.22]{af_primer}, and is equivalent to the statement that the functor
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} \disk_{/N},
    \end{equation}
    %
    is final.
\end{proof}

@@

\begin{lemma}
    Let $u: X \rightarrow \hat{X}$ be the morphism of \cref{ex:forget_strat} that forgets the stratification.
    The functor $u_*: \lcfa_{X} (\catC) \rightarrow \lcfa_{\hat{X}} (\catC)$ has a fully faithful left adjoint.
\end{lemma}

@@

\begin{remark}
    The above proposition also appears as \cite[prop.18]{ginot2015}. The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$. Using \cref{thm:disk_alg=lcfa}, the statement is equivalent to the fact that there is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
    \end{equation}
    %
    with the tensor product of $\infty$-opeards. Again for smooth manifolds this is found in \cite[ex.5.4.5.5]{lurie_ha}. In fact, this version is the one that easily generalizes to the stratified case.
\end{remark}

@@

    For the equivalence, we adapt \cite[ex.5.4.5.5]{lurie_ha}, as mentioned above. Namely, using that technology, the only thing we need to prove is that there is an equivalence between $\infty$-categories induced by the functor
    %
    \begin{align}
        \bsc_{/M} \times \bsc_{/N} &\xrightarrow[\simeq]{\ \ \times \ \ } \bsc_{/M \times N} \notag\\
        ((U \xhookrightarrow{} M), (V \xhookrightarrow{} N)) &\mapsto (U \times V \xhookrightarrow{} M \times N).
    \end{align}
    %
    ......
\end{proof}

\begin{remark}
    The discussion at \cref{rem:fh_is_pushingforward} implies that one way to see the above proposition is as related to the Fubini theorem for factorization homology \cite[cor.2.29]{aft_fhstrat}.
\end{remark}

%\subsection{Inheritance from a Covering Space}

%{\color{red} SHOULD THIS STAY? OR JUST CITE SPHERE RESULT FROM SOMEWHERE}

%We can also induce factorization algebras on a space $X$ if we know how to describe them on a covering space of $X$. The proofs of the statements below require the full machinery regarding pullbacks of factorization algebras, so we will omit them. They can be found in \cite[ch.7.2]{cg2016}. For the extension to the stratified case, see \cite{ginot2015}.

%\begin{definition}
%    Let $G$ be a discrete group that acts on a topological space $X$. A $G$-equivariant factorization algebra on $X$ is a factorization algebra $F \in \falg_X (\catC)$ together with a family of equivalences
%    %
%    \begin{equation}
%        \{ \theta_g : g^*F \xrightarrow{\ \ \simeq \ \ } F \}_{g \in G},
%    \end{equation}
%    %
%    such that $\theta_e = \mathrm{id}$ and $\theta_{g h} = \theta_h \circ h^*(\theta_g): h^* g^* F \xrightarrow{\simeq} F$. We write $(\falg_X (\catC))^G$ for the full $\infty$-subcategory spanned by the $G$-equivariant factorization algebras.
%\end{definition}

%\begin{theorem}[{\cite[prop.4.0.1]{cg2016}}]\label{thm:quotient_fas}
%    Let $X$ be a Hausdorff topological space, and $G$ be a discrete group that has a covering space action on $X$. The pullback along the open immersion $q: X \rightarrow X / G$ is an equivalence of $\infty$-categories
%    %
%    \begin{equation}
%        q^* : \falg_{X / G} (\catC) \xrightarrow{\ \ \simeq \ \ } (\falg_{X} (\catC))^G,
%    \end{equation}
%    %
%    between factorization algebras on the quotient space and $G$-equivariant factorization algebras on the covering space. If $X$ is further a stratified manifold the equivalence restricts to an equivalence of the $\infty$-categories of locally constant factorization algebras
%    %
%    \begin{equation}
%        q^* : \lcfa_{X / G} (\catC) \xrightarrow{\ \ \simeq \ \ } (\lcfa_{X}(\catC))^G.
%    \end{equation} 
%\end{theorem}

@@

\begin{theorem}[{\cite{lurie_ha}...}]
    There is an equivalence of $\infty$-categories between the $\infty$-categories of locally constant factorization algebras on $\mathbb{R}^n$ and $\mathbb{E}_n$-algebras
    %
    \begin{equation}
        \alg{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n} (\catC).
    \end{equation}
\end{theorem}

@@

Specializing \cref{prop:exp_of_products_lc} to the case of Euclidean spaces gives the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}.

@@

\begin{remark}
    The proof of \cref{prop:exp_of_products_lc} given in \cite{ginot2015} actually depends on Dunn additivity to work, instead of the other way around, however the proof presented in \cite{lurie_ha} is independent and thus gives rise to both statements. 
\end{remark}

>>>>

\begin{proposition}\label{prop:fh_disk_to_lcfa}
    Given $M$ a stratified manifold factorization homology provides a functor between the $\infty$-categories of $\disk_{/M}$-algebras and locally constant factorization algebras $\lcfa_M$
    %
    \begin{equation}
        \int : \alg{\disk_M} (\catC) \xrightarrow{\ \ \ \ } \lcfa_M (\catC).
    \end{equation}
\end{proposition}

@@

    Since $\catC$ has all relevant colimits the left Kan extension $\int F$ is given pointwise by
    %
    \begin{equation}\label{eq:pointwiseKan}
        \int_e F \simeq \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} \disk_{/M} \xrightarrow{F} \catC),
    \end{equation}
    %
    so what we need to show is that this colimit is equivalent to the colimit
    %
    \begin{equation}\label{eq:cosheaf_colim_relative}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \rightarrow \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    for each covering sieve $\mathscr{U}$. Since we aren't actually trying to get the value of these colimits we can rewrite \cref{eq:pointwiseKan} into the idiosyncratic form
    %
    \begin{equation}\label{eq:idiosync_form}
        \mathsf{colim} ((\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC),
    \end{equation}
    %
    which is easier to compare to \cref{eq:cosheaf_colim_relative}. Using the fact that $\disk[r]_{/M} \xrightarrow{} \disk_{/M}$ is a final functor, which is a consequence of \cite[prop.2.22]{aft_fhstrat}, and the equivalences of \cref{lem:double_slice} we can rewrite \cref{eq:idiosync_form} further into
    %
    \begin{align}
        \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\disk_{/M})_{/e} \xrightarrow{} (\mfld_{/M})_{/e} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC) \\ \simeq \mathsf{colim} ((\disk[r]_{/M})_{/e} \xrightarrow{} (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC).
    \end{align}
    %
    Denoting the functor $\mfld[r]_{/N} \simeq (\mfld[r]_{/M})_{/e} \xrightarrow{} \mfld[r]_{/M} \xrightarrow{} \mfld_{/M} \xrightarrow{\int F} \catC$ by $K_F$ and comparing with \cref{eq:cosheaf_colim_relative} we need to show
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C) \simeq \mathsf{colim} (\disk[r]_{/N} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{K_F} C),
    \end{equation}
    %
    but this already follows from part 2 of the proof of \cite[prop.2.22]{af_primer}, and is equivalent to the statement that the functor
    %
    \begin{equation}
        \mathsf{colim} (\mathscr{U} \xrightarrow{} \mfld[r]_{/N} \xrightarrow{} \mfld[r] \xrightarrow{\disk_{/-}} \cat) \xrightarrow{} \disk_{/N},
    \end{equation}
    %
    is final.
\end{proof}

@@

\begin{lemma}\label{lem:ff_functor_to_refinement}
    Let $u: X \rightarrow \hat{X}$ be the morphism of \cref{ex:forget_strat} that forgets the stratification.
    The functor $u_*: \lcfa_{X} (\catC) \rightarrow \lcfa_{\hat{X}} (\catC)$ has a fully faithful left adjoint.
\end{lemma}

@@

\begin{remark}
    The above proposition also appears as \cite[prop.18]{ginot2015}. The equivalence proven there is for the case of smooth manifolds and relies on the local proof of \cite{lurie_ha} for $\mathbb{R}^n$. Using \cref{thm:disk_alg=lcfa}, the statement is implied by the fact that there is an equivalence of $\infty$-operads
    %
    \begin{equation}
        \disk_{/M} \otimes \disk_{/N} \xrightarrow{\ \ \simeq \ \ } \disk_{/M \times N},
    \end{equation}
    %
    with the tensor product of $\infty$-opeards. Again for smooth manifolds this is found in \cite[ex.5.4.5.5]{lurie_ha}.
\end{remark}

@@

    One way to show the equivalence is to use factorization homology, as in \cref{thm:disk_alg=lcfa}, to write a locally constant factorization algebra as $\int_{-} A \in \lcfa_{X \times Y} (\catC)$. Then using the Fubini theorem \cite[cor.2.29]{aft_fhstrat}\footnote{The notation used in the citation is technically abusive because factorization homology is evaluating lower dimensional manifolds, but it is clear that this is to be understood exactly as the evaluation of the pushforward factorization algebra on the lower dimensional manifold.} for factorization homology we get essential surjectivity because there are equivalences
    %
    \begin{equation}
        \int_{U \times V} A \xrightarrow{\ \ \simeq \ \ } \int_U \int_V \bar{\pi} A
    \end{equation}
    %
    between objects of $\catC$. As argued in the proof of \cref{thm:disk_alg=lcfa}, these equivalences are natural in the open set variables, which means that they rise to equivalences at the level of locally constant factorization algebras. In fact, looking at the proof of \cite[thm.2.25]{aft_fhstrat}, which is what underlies the construction of the above equivalences, we see that they arise from an argument about a final functor. By \cref{rem:fin_equiv_natural} this means that the equivalences are actually natural in the algebra variable, so it is immediate that the equivalences of individual locally constant factorization algebras lift to a full equivalence of $\infty$-categories.
\end{proof}

@@

\begin{theorem}[{\cite[thm.5.5.4.10]{lurie_ha}}]
    There is an equivalence of $\infty$-categories between the $\infty$-categories of locally constant factorization algebras on $\mathbb{R}^n$ and $\mathbb{E}_n$-algebras
    %
    \begin{equation}
        \alg{\mathbb{E}_n} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{\mathbb{R}^n} (\catC).
    \end{equation}
\end{theorem}

@@

We can view a Euclidean space $\mathbb{R}^{m+n}$ as a product space $\mathbb{R}^m \times \mathbb{R}^n$, in which case \cref{prop:exp_of_products_lc} specializes to give the famous result of Dunn additivity \cite{dunn1988} which can be found in the following form in \cite{lurie_ha}:

@@

\begin{remark}
    The proof of \cref{prop:exp_of_products_lc}, when specialized to ordinary manifolds, as given in \cite{ginot2015} actually depends on Dunn additivity to work, however the proof presented in \cite{lurie_ha} is independent. 
\end{remark}
